\section{Phases of work}
In this section the different phases of the tendering will be elaborated. 

\subsection*{Discovery}
In this phase the contractor shall identify the needed hardware such as the best microprocessor-system, best battery option, materials for housing, hardware for telecommunications and available sensors on the market. 

\subsection*{Design}
The design phase will contain the design of the hand-held device. This shall include all interfaces and specific hardware design documents. 
If elected the contractor shall provide documentation according to a later specified agreement. 

\subsection*{Development and Production}
The development and integration of the hand-held device is a joint operation between the contractor and Dunke Inc. The production will be the contractors responsibility including any hardware and OS specific tests. 

\subsection*{Testing}
During this phase extensive testing will be required. In the response proposal an outline for these tests shall be quoted. 

\section{Development guidelines and requirements}
\label{sec:guidelines_and_requirements}
The following requirements encapsulates functionality regarding both software and hardware. Therefore you shall extract the appropriate information from the requirements below in order to design and develop an adequate hardware platform.

\subsection{Capability requirements}
\begin{description}
\item[FR-0111] The hand-held dismounted COP shall be able to get its current location.
\item[FR-0112] The hand-held dismounted COP shall be able to notify the server with the current location. 
\end{description}


\subsection{Safety requirements }
\begin{description}
\item[FR-0350] The hand-held dismounted COP shall warn the user about dangerous radiation
levels.
\item[ FR-0352] The hand-held dismounted COP shall warn the user about dangerous
temperature levels.
\item[FR-0354] The hand-held dismounted COP shall warn the user about dangerous oxygen
levels.
\end{description}
 
 
\subsection{System environment requirements}
\begin{description}
\item[FR-0390] The hand-held dismounted COP shall be waterproof.
\item[FR-0400] The hand-held dismounted COP shall be shock resistant.
\item[FR-0410] The hand-held dismounted COP shall be heat resistant.
\item[FR-0420] The hand-held dismounted COP shall be cold resistant.
\end{description}

\subsection{System quality factors}
\begin{description}
\item[FR-0430] Warranty period shall be at least 10 years.
\item[FR-0440] The system shall be open for future updates.
\end{description}

\subsection{Design and construction constraints}
\begin{description}
\item[FR-0460] The hand-held dismounted COP shall be wearable. 
\item[FR-0470] The hand-held dismounted COP shall be worn so it is easily accessible.
\end{description}

\subsection{Non-functional requirements}
\begin{description}
\item[NFR-0131] The location of a device shall able to be updated at least every 10 seconds (FR-0110).
\item[NFR-0140] When the system provides COP-information to a device, the information must
be available on the device within 10 seconds (FR-0115).
\item[NFR-0170] Dangerous radiation levels are defined by measurements above 0.25 Sievert.
\item[NFR-0180] Dangerous temperature levels are defined by temperatures below -40 °C and
above 70 °C (FR-0352).
\item[NFR-0190] Dangerous oxygen levels are defined by oxygen levels below 10 % of the
atmosphere (FR-0354).
\item[NFR-0200] The probability of data loss shall not exceed 1/1000 (FR-0450).
\item[NFR.0210] The weight of the hand-held dismounted COP shall not exceed 1 kg (FR-0460).
\end{description}



\section{Reporting during joint operations}
The contractor will be obliged to give regular updates. Typically on a weekly basis or similar. It will be the forum for discussion of problems and solutions. 

In the end of every phase the contractor shall provide documentation that summarizes the work conducted in the phase.