\chapter{Background and description}
\section{Background}
In a crisis situation, the SitaWare Civilian allows communication and exchange of information between various users. The following is a list of the relevant users who can improve their level of communication and intelligence during a crisis situation:

\begin{enumerate}
\item[•] The Fire Department
\item[•] The Police Department
\item[•] The Search and Rescue Department
\item[•] The Emergency Management Agency
\item[•] The Health Management Agency
\item[•] The Environment Management Agency
\item[•] The Marine Environment Management Agency
\item[•] Armed Forces
\end{enumerate}

\section{Vision}
The effectiveness of an emergency management team deployed on the location of a crisis
situation is greatly dependent on the team’s situational awareness. The more emergency
response actors involved in a crisis situation, the higher is the risk of losing overview and
control of the situation. The lack of overview might end up in important information
getting lost and missions being carried out in undesirable ways.
A way of getting this to every actor in the emergency team is by introducing a condensed common operation picture in a hand-held device. 

\subsection{Description of project}
Create the hardware platform for a hand-held condensed COP. The device shall be able to be mounted on the users arm. It shall be resilient to harsh environments and be reliable in use. The hand-held COP shall have a intuitive touchscreen interface and able to connect with the rest of the system through telecommunication.
The hand-held device shall embed various sensors and have sufficient battery to be used several days. 

