\chapter{Introduction}
\section{Summary}
Dunke Inc. is accepting proposals to develop the hardware for a specific hand-held dismounted COP. The assignment will be based on requirements given by Dunke Inc. By these requirements the contractor will design, develop and produce the hand-held device hardware. 

\section{Proposal guidelines and requirements}

\begin{enumerate}

\item[•]The selection of contractor is a closed but competitive process. Only invited contractors will be subject to evaluation. 
\item[•]Proposals shall be received by Dunke Inc. before TIME, DAY AND DATE, YEAR. Proposals which are received after will not be subject for evaluation. \fxfatal{indsæt tid, dato og år.}
\item[•]It shall contain the signature of a authorized officer to verify the proposal. 
\item[•]Prices quoted in the proposal shall be fully explained.
\item[•]The RFP is a confidential document and all information regarding this project is only for classified personnel. 
\end{enumerate}


\section{Contract terms}
Upon selected to subcontract Dunke Inc. will draft a initially contract. This contract will be available for the subcontractors legal department for investigation and signing. 

The project will start on the DATE and is expected to be finished at the latest of the DATE \fxfatal{indsæt dato} 

Any subcontracting is allowed by Dunke Inc. but this shall be explicit explained in the proposal response. 
Subcontractors and their work must be quoted in details. 
Though Dunke Inc. will reserve the right to raise objections against a subcontractor and eventually reject a proposal with the subcontractor. 

\section{Payment model and incentives}
The payment will be paid in bites. 
\begin{enumerate}
\item[•] To conduct the discovery and design phase 25-35\% will paid in advance. 
\item[•] Upon starting production phase 65-75\% will be paid. 
\item[•] The remaining will depend on the tests result and the cooperation as a whole.
\end{enumerate}

In total the estimated budget will be around 8-10.000.000,- danish kroner. 