% Capability requirements
\section{Capability Requirements}
\textbf{Precondition}
\begin{itemize}
\item Ten users in ten different locations.
\item Minimum ten devices. 
\item Each type of platform currently employed by various users. \\
\end{itemize}


\begin{description}

\item\textbf{ST-0105} Deploy ten users to ten different locations. No user shall be within 500 meters of each other. Confirm that the system shows the correct location of 10 users. 
\item\textbf{ST-0110} Send COP-information to all devices in use and verify that the information on the COP is in fact the information being sent. 
\item\textbf{ST-0115} Start the devices, and verify that the COP contains information about human population density. 
\item\textbf{ST-0120} Start the devices, and verify that the COP contains typographic information. 
\item\textbf{ST-0125} Start the devices, and verify that the COP contains traffic information. 
\item\textbf{ST-0130} Start the devices, and verify that the COP contains infrastructure information. 
\item\textbf{ST-0135} Start the devices, and verify that the COP contains freshwater locations for firefighting purposes. 
\item\textbf{ST-0140} Register an event on a device. Verify that the registered event is available on another device. 
\item\textbf{ST-0145} Start a device and verify that it contains weather information. 
\item\textbf{ST-0150} Start a device which is running the COP, verify that the information can be filtered using the GUI. 
\item\textbf{ST-0155} Start a device and verify that previous events can be viewed. 
\item\textbf{ST-0160} Register an event from each type of platform currently employed by various users. 
\item\textbf{ST-0165} Start a device and verify that information can be sent to each type of platform currently employed by various users. 
\item\textbf{ST-0170} Send a message to a specific geographical location, and confirm that only devices in this location receives the message. 
\item\textbf{ST-0175} Send a message to a specific device role, and confirm that only devices with this role receives the message. 
\item\textbf{ST-0180} Send a message to a specific device group, and confirm that only devices in this group receives the information.
\item\textbf{ST-0185} Send a message to a specific device identity, and confirm that only devices with this identity receives the information. 

\end{description}

