% Non-functional_requirements
\section{Non-functional Requirements}

\textbf{Preconditions}
\begin{itemize}
\item Timer
\item Test program that puts the system in an error state
\item Weight
\item Temperature cabinet capable of going from -50°C to 80°C in steps of $0.1\frac{^{\circ}C}{min}$
\item Radiation cabinet capable of going from $0.20 Sievert$ to $0.30 Sievert$ in steps of $0.01\frac{Sievert}{min}$
\item Oxygen cabinet capable of going from $60 \%$ to $80 \%$ in steps of $0.1\frac{\%}{min}$
\item BERT equipment
\item The server must be turned on and ready to communicate with the devices
\item Internet connection must be available for all devices in the system
\end{itemize}
~\

\begin{description}
\item[ST-1110] Turn on the system and start a timer. When the system is ready to respond to user input stop the timer. Verify that the time passed is less than 5 minutes.

\item[ST-1120]Write a test program that gets the system to enter an error state. Verify that the a red indicator is shown. 

\item[ST-1130] Turn off the system and start a timer. When the system powers off stop the timer. Verify that the time passed is less than 5 minutes.

\item[ST-1140]Move the hand-held dismounted COP more than 100 meters within 10 seconds and stop moving. Verify that the location of the device registered in the system is updated within 10 seconds after stop. 

\item[ST-1150]Post COP-information from the system to a device and start a timer. When the information is available on the device stop the timer. Verify that the time passed is less than 10 seconds. 

\item[ST-1160]Register information from a device to the system and start a timer. When the registered information is available on the other devices stop the timer. Verify that the time passed is less than 15 seconds. 

\item[ST-1170] Post weather information from the system to a device and start a timer. When the information is available on the device stop the timer. Verify that the time passed is less than 10 seconds. 

\item[ST-1180] Place the dismounted COP in the radiaton cabinet and expose it to $0.20 Sievert$ and increase the radiation up to $0.30 Sievert$ in steps of $0.01\frac{Sievert}{min}$. Confirm that the dismounted COP warns the user about dangerous radiation levels via the GUI and the audio interface when the measured radiation level exceeds $0.25 Sievert$. 

\item[ST-1190] Place the dismounted COP in the temperature cabinet and expose it to $-30^{\circ}C$ and decrease the temperature down to $-50^{\circ}C$ in steps of $0.1\frac{^{\circ}C}{min}$. Confirm that the dismounted COP warns the user about dangerous temperature levels via the GUI and the audio interface when the measured temperature is below $-40^{\circ}C$.\\
Place the dismounted COP in the temperature cabinet and expose it to $60^{\circ}C$ and increase the temperature up to $80^{\circ}C$ in steps of $0.1\frac{^{\circ}C}{min}$. Confirm that the dismounted COP warns the user about dangerous temperature levels via the GUI and the audio interface when the measured temperature is above $70^{\circ}C$. 

\item[ST-1200] Place the dismounted COP in the oxygen cabinet and expose it to an oxygen level of $5\%$. Increase the oxygen level up to $15\%$ in steps of $0.1\frac{\%}{min}$. Confirm that the dismounted COP warns the user about dangerous oxygen levels via the GUI and the audio interface when the measured oxygen level is above $10\%$. 

\item[ST-1210] Perform a bit error rate test (BERT) of the data communication and verify that it has a bit error rate (BER) of $10^{-3}$ or less. 

\item[ST-1220] Weigh the hand-held dismounted COP. Verify that the weight does not exceed $1kg$. 

\end{description}


