\section{Capability requirements}
%Vi skal have lavet en device description og måske en user description --Peter
%Vi skal have lavet en beskrivelse af hvad observations og events er --Peter

\begin{description}
  \item[FR-0110] The system shall keep track of the location of all devices.
  \item[FR-0115] The system shall be capable of providing all devices with COP-information.
  \item[FR-0120] COP-information shall contain information about human population density.
  \item[FR-0130] COP-information shall contain topographic information.
  \item[FR-0140] COP-information shall contain traffic information.
  \item[FR-0150] COP-information shall contain information of infrastructure.
  \item[FR-0160] COP-information shall contain information of fresh water locations for fire fighting purposes.
  \item[FR-0170] The system shall be capable of providing all devices with observations registered by a user. %Reference til den specifikke bruger af et Dismounted device --Peter
  \item[FR-0180] The system shall be capable of providing all devices with weather information.
  \item[FR-0190] The system shall allow all users to selectively exclude specific COP-information.
  \item[FR-0200] The system shall allow all users to view previous events submitted by a user.
  \item[FR-0210] The system shall be able to register events using the platforms currently employed by the various users.
  \item[FR-0220] The system shall be able to send information to the platforms currently employed.
  \item[FR-0230] The system shall be able to distribute messages based on geographic information.
  \item[FR-0240] The system shall be able to distribute messages based on role information.
  \item[FR-0250] The system shall be able to distribute messages based on group information.
  \item[FR-0260] The system shall be able to distribute messages based on identity information.

\end{description}